---
title: "Square of Polynomial - Functions"
author: "Oliver Vu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  out.width = "80%",
  cache = TRUE
)
```

## Introduction 

This vignette provides an overview of a set of polynomial functions of degree 2, including:

1. `find_root()`: Finds the root of the polynomial.
2. `find_min()`: Finds the minimum value of the polynomial.
3. `find_max()`: Finds the maximum value of the polynomial.
4. `plot_polynomial()`: Visualizes the polynomial on a graph.
5. `get_y_value()`: Finds the value of the polynomial at a given x-value.

## Functions

### Find Root 

```{r}
find_roots <- function(a, b, c) {
  d <- b^2 - 4*a*c
  if (d < 0) {
    return(NULL)
  } else if (d == 0) {
    return(-b / (2*a))
  } else {
    return(c((-b + sqrt(d)) / (2*a), (-b - sqrt(d)) / (2*a)))
  }
}

```

### Find Minimum 

```{r}
find_min <- function(a, b, c) {
  if (a > 0) {
    return(c - (b^2) / (4 * a))
  } else {
    return(NA)
  }
}
```

### Find Maximum 

```{r}
find_max <- function(a, b, c) {
  if (a < 0) {
    return(c - (b^2) / (4 * a))
  } else {
    return(NA)
  }
}
```

### Visualize x with y

```{r}
visualize <- function(a, b, c) {
  x <- seq(-10, 10, length.out = 100)
  y <- a*x^2 + b*x + c
  plot(x, y, type = "l", xlab = "x", ylab = "y")
}
```

### Get y value 

```{r}
get_y <- function(a, b, c, x) {
  return(a*x^2 + b*x + c)
}
```

## Example Usage 

#### `find_root()` 

```{r}
# Load the package
library(squarepolynomial)

# Find the root
find_root(1, -3, 2)
```

#### `find_min()` and `find_max()`

```{r}
# Load the package
library(squarepolynomial)

# Find the minimum value
find_min(1, -3, 2)

# Find the maximum value
find_max(1, -3, 2)
```

#### `visualize()` 

```{r}
# Load the package
library(squarepolynomial)

# Visualize the polynomial
visualize(1, -3, 2)
```

#### `get_y()`

```{r}
# Load the package
library(squarepolynomial)

# Find the value of the polynomial at x = 2
get_y(1, -3, 2, 2)
```

## Conclusion 

This vignette has provided an overview of a set of polynomial functions of degree 2. These functions can be useful for a variety of applications, including optimization, visualization, and analysis of data.



