---
title: "Easy Test"
author: "Oliver Vu" 
output: html_document
date: '2023-03-02'
---

```{r setup, include=FALSE}
library(leaflet)
library(dplyr)
library(leaflet)
library(leaflet.extras)
library(RColorBrewer)
library(lubridate)
library(shiny)
library(shiny)
library(leaflet)
library(RColorBrewer)
```

#### Test Description: Download the leaflet package and demonstrate it with a naturally occurring time series. Document it with RMarkdown.

### 1. Creating an interactive map visualising earthquake data using the `quakes` dataset. 

```{r}
# Load example data
data(quakes)

# Create leaflet map
leaflet(quakes) %>%
  addTiles() %>%
  addMarkers(
    popup = ~paste(
      "<strong>Location:</strong> ", quakes$lat, ", ", quakes$long, "<br>",
      "<strong>Magnitude:</strong> ", quakes$mag, "<br>",
      "<strong>Depth:</strong> ", quakes$depth, "km"
    ),
    label = ~as.character(quakes$mag)
  ) %>%
  addLegend(
    "bottomright",
    title = "Magnitude",
    colors = c("green", "yellow", "red"),
    labels = c("4-5", "5-6", "6+")
  ) %>%
  addProviderTiles("Esri.NatGeoWorldMap") %>%
  addMiniMap()

```


### 2. Creating an interactive map visualising a mock dataset of a property company.  

```{r}

df2 <- read.table(header = T, text = '
latitude	longitude	Flat	Land	Office
42.85	-2.6727	5	22	25
38.3452	-0.4815	2	24	25
38.161	-0.8013	5	17	11
38.1631	-0.8115	5	22	24
38.1673	-0.8034	5	15	13
38.1776	-0.7973	5	21	16
37.9787	-0.6822	2	11	16
38.2622	-0.7011	61	24	16
39.9333	-0.1	0	14	13
38.0848	-0.944	0	21	21
38.125	-0.8782	3	18	14
38.1339	-0.8624	3	12	15
38.1518	-0.8308	3	21	20
38.6253	-0.5722	3	14	14
')

leaflet(df2) %>%
  addTiles() %>%
  addMarkers(lat = ~latitude, lng = ~longitude, 
             clusterOptions = markerClusterOptions(zoomToBoundsOnClick = T), 
              icon = list(
               iconUrl = 'https://colepowered.com/wordpress/wp-content/uploads/2014/10/29102014-8.png',
               iconSize = c(75, 75)),
             popup = ~paste(
               paste('<b>', 'Flat:', '</b>', Flat), 
               paste('<b>',  'Land:', '</b>', Land),
               paste('<b>', 'Office:', Office),
               sep = '<br/>'),
             popupOptions = popupOptions(closeButton = FALSE)
             )
```


### 3. Creating an interactive map of earthquake data using `Shiny` and `Leaflet` 
```{r}


ui <- bootstrapPage(
  tags$style(type = "text/css", "html, body {width:100%;height:100%}"),
  leafletOutput("map", width = "100%", height = "100%"),
  absolutePanel(top = 10, right = 10,
    sliderInput("range", "Magnitudes", min(quakes$mag), max(quakes$mag),
      value = range(quakes$mag), step = 0.1
    ),
    selectInput("colors", "Color Scheme",
      rownames(subset(brewer.pal.info, category %in% c("seq", "div")))
    ),
    checkboxInput("legend", "Show legend", TRUE)
  )
)

server <- function(input, output, session) {

  # Reactive expression for the data subsetted to what the user selected
  filteredData <- reactive({
    quakes[quakes$mag >= input$range[1] & quakes$mag <= input$range[2],]
  })

  # This reactive expression represents the palette function,
  # which changes as the user makes selections in UI.
  colorpal <- reactive({
    colorNumeric(input$colors, quakes$mag)
  })

  output$map <- renderLeaflet({
    # Use leaflet() here, and only include aspects of the map that
    # won't need to change dynamically (at least, not unless the
    # entire map is being torn down and recreated).
    leaflet(quakes) %>% addTiles() %>%
      fitBounds(~min(long), ~min(lat), ~max(long), ~max(lat))
  })

  # Incremental changes to the map (in this case, replacing the
  # circles when a new color is chosen) should be performed in
  # an observer. Each independent set of things that can change
  # should be managed in its own observer.
  observe({
    pal <- colorpal()

    leafletProxy("map", data = filteredData()) %>%
      clearShapes() %>%
      addCircles(radius = ~10^mag/10, weight = 1, color = "#777777",
        fillColor = ~pal(mag), fillOpacity = 0.7, popup = ~paste(mag)
      )
  })

  # Use a separate observer to recreate the legend as needed.
  observe({
    proxy <- leafletProxy("map", data = quakes)

    # Remove any existing legend, and only if the legend is
    # enabled, create a new one.
    proxy %>% clearControls()
    if (input$legend) {
      pal <- colorpal()
      proxy %>% addLegend(position = "bottomright",
        pal = pal, values = ~mag
      )
    }
  })
}

shinyApp(ui, server)
```


